---
title: "Dimensionality Analyses of the Character Judgments"
author: "Pooya Razavi"
date: "last knitted: `r Sys.time()`"
output: 
  html_document:
    theme: cosmo
    highlight: textmate
    toc: TRUE
    toc_float: TRUE
editor_options: 
  chunk_output_type: console
---

```{r import-data, include=FALSE}
library(tidyverse)

#read in the datafile
df <- readxl::read_xlsx("Perc_AngExpress_2datasets.xlsx")


#reading in the variable names
var_name_df <- readxl::read_xlsx("variable_names.xlsx")

knitr::opts_chunk$set(echo = TRUE)
```

# Data Preparation

```{r data-cleaning}
#remove rows that are all NAs
df_na_removed <- df %>% 
                    dplyr::filter(!if_all(c(Q20_1, Q70), is.na))

#the original column names (imported from Qualtrics) 
dplyr::glimpse(df[,1:20])


#use the variable names (from the external file) to rename data columns from Qualtrics labels to the character judgments
colnames(df_na_removed) <- var_name_df$var_name


#now the column names are easier to follow
dplyr::glimpse(df[,1:20])

```

Each participant provided multiple ratings. Before combining all the ratings into a long format, we want to mean-center them, because we don't want mean differences between the conditions to artificially influence the factor structure. Below, I'll create a dataframe with mean-centered ratings just for the dimensionality analyses.

```{r mean-centering}

ratings_centered <- df_na_removed %>% 
                        select(inf_s_m_y_capable.leader:rud_o_f_y_community.work) %>% 
                        scale(., scale = FALSE) %>% 
                        as_tibble()


#check a couple of columns to show that the mean is indeed zero 
mean(ratings_centered$inf_s_m_y_capable.leader, na.rm = TRUE)
mean(ratings_centered$rud_s_f_n_loyal.truehearted, na.rm = TRUE)
```




```{r long-ish-df}

ratings_centered_longish <- ratings_centered %>% 
                              tibble::rowid_to_column() %>% 
                              tidyr::pivot_longer(data = .,
                                                  cols = !rowid) %>% 
                              separate(name, c("senario", "harm_target", "prot_gender", "anger_express", "col"), 
                                       sep = "_") %>% 
                              tidyr::pivot_wider(data = .,
                                                 names_from = col,
                                                 values_from = value)
                              

#remove the row where all ratings are NA
ratings_centered_longish <- ratings_centered_longish %>% 
                                  dplyr::filter(!if_all(c(capable.leader, community.work), is.na))


```


# Correlation between Ratings

To avoid bloated specifics, lets find very highly correlated ratings (i.e., r > .65).

```{r intercorrelations}
ratings_centered_longish %>% 
  select(capable.leader:community.work) %>% 
  rstatix::cor_mat() %>% 
  rstatix::cor_gather(drop.na = TRUE) %>% 
  mutate(strong_cor = if_else(cor >= .65, "yes", "no")) %>% 
  filter(strong_cor == "yes" & cor < 1)
```

"Brave" and "capable of leadership" are highly correlated; so are "honorable" and "noble." From the first pair, I'll keep "brave," and from the second one, I'll keep "honorable."

# Determining the Number of Factors

Determining the optimal number of factors using screeplot, parallel analyses and other methods from the _psych_ package. Different methods suggest that 2-, 4-, and 9-factor structures are plausible solutions.

## Scree plot

```{r scree-plot}
#seems like 4- or 5- factors or components are reasonable solutions
ratings_centered_longish %>% 
  select(capable.leader:community.work) %>% 
  select(!c(capable.leader, noble)) %>% 
  psych::scree()

```

## Parallel analysis

```{r parallel-analysis}
#Parallel analysis suggests that the number of factors =  8  and the number of components =  4 
ratings_centered_longish %>% 
  select(capable.leader:community.work) %>% 
  select(!c(capable.leader, noble)) %>% 
  psych::fa.parallel()


```

## Velicor's MAP

```{r velicor-VSS}

#The Velicer's MAP suggests a 4-factor structure. Other methods suggest up to 9 components 

ratings_centered_longish %>% 
  select(capable.leader:community.work) %>% 
  select(!c(capable.leader, noble)) %>% 
  psych::nfactors(n = 9)

```


# Examining Multiple Structural Solutions

Based on what the previous analyses, we should examine different structures ranging from 2- to 9-component solutions.

## 2 components

The two-component structure boils down to positive vs. negative characteristics.

```{r two-component-str}
pca_2_component <- ratings_centered_longish %>% 
                        select(capable.leader:community.work) %>% 
                        select(!c(capable.leader, noble)) %>% 
                        psych::principal(., nfactors = 2, rotate = "varimax") 
        
two_comp_outcome <- psych::kaiser(pca_2_component, rotate = "Varimax") %>% psych::fa.sort()

two_comp_outcome[["loadings"]] %>% 
                  knitr::kable(digits = 2) %>%
                  kableExtra::kable_styling(bootstrap_options = c("striped", "hover")) %>% 
                  kableExtra::kable_paper(full_width = F)

```

## 3 components

```{r three-component-str}
pca_3_component <- ratings_centered_longish %>% 
                        select(capable.leader:community.work) %>% 
                        select(!c(capable.leader, noble)) %>% 
                        psych::principal(., nfactors = 3, rotate = "varimax") 
        
three_comp_outcome <- psych::kaiser(pca_3_component, rotate = "Varimax") %>% psych::fa.sort()

three_comp_outcome[["loadings"]] %>% 
                  knitr::kable(digits = 2) %>%
                  kableExtra::kable_styling(bootstrap_options = c("striped", "hover")) %>% 
                  kableExtra::kable_paper(full_width = F)
```


## 4 components

We see a clearly interpretable set of components here. Consistent with the scree test and Velicor's MAP, it seems that the four-component structure is sensible.

```{r four-component-str}
pca_4_component <- ratings_centered_longish %>% 
                        select(capable.leader:community.work) %>% 
                        select(!c(capable.leader, noble)) %>% 
                        psych::principal(., nfactors = 4, rotate = "varimax") 
        
four_comp_outcome <- psych::kaiser(pca_4_component, rotate = "Varimax") %>% psych::fa.sort()

four_comp_outcome[["loadings"]] %>% 
                  knitr::kable(digits = 2) %>%
                  kableExtra::kable_styling(bootstrap_options = c("striped", "hover")) %>% 
                  kableExtra::kable_paper(full_width = F)
```


```{r four-component-str-v2}
pca_4_component_v2 <- ratings_centered_longish %>% 
                        select(capable.leader:community.work) %>% 
                        select(!c(capable.leader, noble)) %>% 
                        select(!c(modest)) %>% 
                        psych::principal(., nfactors = 4, rotate = "varimax") 
        
four_comp_outcome_v2 <- psych::kaiser(pca_4_component_v2, rotate = "Varimax") %>% psych::fa.sort()

four_comp_outcome_v2[["loadings"]] %>% 
                  knitr::kable(digits = 2) %>%
                  kableExtra::kable_styling(bootstrap_options = c("striped", "hover")) %>% 
                  kableExtra::kable_paper(full_width = F)
```


```{r four-component-str-v3}
pca_4_component_v3 <- ratings_centered_longish %>% 
                        select(capable.leader:community.work) %>% 
                        select(!c(capable.leader, noble)) %>% 
                        select(!c(modest, religious)) %>% 
                        psych::principal(., nfactors = 4, rotate = "varimax") 
        
four_comp_outcome_v3 <- psych::kaiser(pca_4_component_v3, rotate = "Varimax") %>% psych::fa.sort()

four_comp_outcome_v3[["loadings"]] %>% 
                  knitr::kable(digits = 2) %>%
                  kableExtra::kable_styling(bootstrap_options = c("striped", "hover")) %>% 
                  kableExtra::kable_paper(full_width = F)
```

## 5 components

We start to see the potential signs of over-factoring here. The last component consists of only 1 item.


```{r five-component-str}
pca_5_component <- ratings_centered_longish %>% 
                        select(capable.leader:community.work) %>% 
                        select(!c(capable.leader, noble)) %>% 
                        psych::principal(., nfactors = 5, rotate = "varimax") 
        
five_comp_outcome <- psych::kaiser(pca_5_component, rotate = "Varimax") %>% psych::fa.sort()

five_comp_outcome[["loadings"]] %>% 
                  knitr::kable(digits = 2) %>%
                  kableExtra::kable_styling(bootstrap_options = c("striped", "hover")) %>% 
                  kableExtra::kable_paper(full_width = F)
```

## 6 components 

We see more indications of potential over-factoring. This time, the fifth component consists of a single item (i.e., "indifferent"), and there's an increase in the number of cross-loading items.

```{r six-component-str}
pca_6_component <- ratings_centered_longish %>% 
                        select(capable.leader:community.work) %>% 
                        select(!c(capable.leader, noble)) %>% 
                        psych::principal(., nfactors = 6, rotate = "varimax") 
        
six_comp_outcome <- psych::kaiser(pca_6_component, rotate = "Varimax") %>% psych::fa.sort()

six_comp_outcome[["loadings"]] %>% 
                  knitr::kable(digits = 2) %>%
                  kableExtra::kable_styling(bootstrap_options = c("striped", "hover")) %>% 
                  kableExtra::kable_paper(full_width = F)
```

## 7 components

Has a couple of components with a single item, and some cross-loading items.

```{r seven-component-str}
pca_7_component <- ratings_centered_longish %>% 
                        select(capable.leader:community.work) %>%
                        select(!c(capable.leader, noble)) %>%  
                        psych::principal(., nfactors = 7, rotate = "varimax") 
        
seven_comp_outcome <- psych::kaiser(pca_7_component, rotate = "Varimax") %>% psych::fa.sort()

seven_comp_outcome[["loadings"]] %>% 
                  knitr::kable(digits = 2) %>%
                  kableExtra::kable_styling(bootstrap_options = c("striped", "hover")) %>% 
                  kableExtra::kable_paper(full_width = F)
```

## 8 components

Cross-loading items keep increasing.

```{r eight-component-str}
pca_8_component <- ratings_centered_longish %>% 
                        select(capable.leader:community.work) %>% 
                        select(!c(capable.leader, noble)) %>% 
                        psych::principal(., nfactors = 8, rotate = "varimax") 
        
eight_comp_outcome <- psych::kaiser(pca_8_component, rotate = "Varimax") %>% psych::fa.sort()

eight_comp_outcome[["loadings"]] %>% 
                  knitr::kable(digits = 2) %>%
                  kableExtra::kable_styling(bootstrap_options = c("striped", "hover")) %>% 
                  kableExtra::kable_paper(full_width = F)

```


## 9 components

9-component structure has multiple cross-loading item; removing them will leave some components with a single item. Potential indications that too many components are extracted.

```{r nine-component-str}
pca_9_component <- ratings_centered_longish %>% 
                        select(capable.leader:community.work) %>%
                        select(!c(capable.leader, noble)) %>%  
                        psych::principal(., nfactors = 9, rotate = "varimax") 
        
nine_comp_outcome <- psych::kaiser(pca_9_component, rotate = "Varimax") %>% psych::fa.sort()

nine_comp_outcome[["loadings"]] %>% 
                  knitr::kable(digits = 2) %>%
                  kableExtra::kable_styling(bootstrap_options = c("striped", "hover")) %>% 
                  kableExtra::kable_paper(full_width = F)
```

# Optimal Structure

Considering these results, it seems that the following 4-component structure is the most interpretable, and fewer issues in terms of number of items per dimension and cross-loading items.

## Loadings 

```{r four-comp-item-loadings}
four_comp_outcome_v3[["loadings"]] %>% 
                  knitr::kable(digits = 2) %>%
                  kableExtra::kable_styling(bootstrap_options = c("striped", "hover")) %>% 
                  kableExtra::kable_paper(full_width = F)
```

## Visualization

```{r four-comp-visual, fig.height=9, fig.width=10}
four_comp_df <- four_comp_outcome_v3[["loadings"]] %>% 
            as.data.frame() %>% 
            tibble::rownames_to_column(., "Trait")

four_comp_df$Trait <- factor(four_comp_df$Trait, levels = four_comp_df$Trait) #this is needed to that ggplot doesn't rearrange the order of rating items alphabetically

four_comp_df_long <- four_comp_df %>% 
                          tidyr::pivot_longer(data = .,
                                cols = starts_with("RC"),
                                names_to = "Component",
                                values_to = "Loading")

four_comp_df_long %>% 
  ggplot(aes(x = Trait, y = Loading, fill = Component)) +
        geom_bar(stat = "identity") +
        scale_x_discrete(limits = rev(levels(four_comp_df$Trait))) +#reverse the order of the item labels
        facet_wrap(~Component) +
        coord_flip()


#in case you want to try a different method where each component is graphed separately
comp1_fig <- four_comp_df %>% 
                ggplot(aes(x = Trait, y = RC1)) +
                geom_bar(stat = "identity") +
                scale_x_discrete(limits = rev(levels(four_comp_df$Trait))) + #reverse the order of the item labels
                coord_flip() 


```

## Scoring and reliability

```{r scoring-reliability}

ratings_longish <- df_na_removed %>% 
                              #tibble::rowid_to_column() %>% 
                              tidyr::pivot_longer(data = .,
                                                  cols = inf_s_m_y_capable.leader:rud_o_f_y_community.work) %>% 
                              separate(name, c("senario", "harm_target", "prot_gender", "anger_express", "col"), 
                                       sep = "_") %>% 
                              tidyr::pivot_wider(data = .,
                                                 names_from = col,
                                                 values_from = value)
                              

#remove the row where all ratings are NA
ratings_longish <- ratings_longish %>% 
                                  dplyr::filter(!if_all(c(capable.leader, community.work), is.na))



ratings_key <- list(
  social_conscience = c("helpful.others", "willing.sacrifice", "admired", "respected", "community.work",
                        "loyal.truehearted", "grateful", "honorable", "keeps.promises", "values.relations",
                        "virtuous", "fits.customs"),
  steadfastness = c("not.allow.oppress", "high.selfesteem", "not.compromise.principles", "honest", "brave",
                    "persistent.steadfast", "-indifferent"),
  wisdom = c("acts.calculated", "has.selfcontrol", "wise", "intellectual"),
  obstinacy = c("pessimistic.suspicious", "holds.grudges", "stubborn", "dogmatic", "hypocrite")
)

#calculate scale scores
      judgment.categories <- psych::scoreItems(ratings_key, ratings_longish, impute = "none")
#internal consistencies and intercorrelations
      judgment.categories

ratings_longish <- cbind(ratings_longish, judgment.categories$scores) 

```

